---
title: "A1_Vignette"
author: "MIngyang Li"
date: "11/4/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First of all, to be able use the functions in the functions.R, the following 
packages are required.
```{r}
library(imager)
library(tidyverse)
library(tidymodels)
library(sp)
library(scales)
library(cowplot)
devtools::install_github("sharlagelfand/dmc")
library(dmc)
```
```{r}
#After the above packages are successfully loaded, we can load our functions by
#using the command below.
source("functions.R")
set.seed(1004931425)
```
The first function you need to use is process_image(). It takes an image file 
name and a list of k as input. It is noteworthy that the function can be only 
used on a JPEG or PNG file. The k_list is the list of numbers of colors that you
decide for your cross-stitich pattern. For example, if we choose the k_list to 
be c(2, 4, 6), then you are planing on to have two or four or six colors on your
cross-stitich pattern.
```{r}
k_list <- c(2:8) # This means you are choosing between two to eight thread colors.
cluster_info <- process_image("minion.jpg", k_list)
```

```{r}
#The following command is only for illustrating the image.
img <- load.image("minion.jpg")
plot(img)
```

After process_image() is successfully executed, we will have all the information 
stored in the cluster_info. To be specific, the cluster_info contains clustering 
information for each k chosen in the list, the RGB values and hex values 
of the original image, and the tidied clusters with their associated 
RGB values and their nearest DMC thread colour hex values.
```{r}
cluster_info[[1]]
```
```{r}
cluster_info[[2]]
```
```{r}
cluster_info[[3]]
```

Then, we use scree_plot() to get a plot of total within cluster sum of squares 
versus ks.
```{r}
scree_plot(cluster_info)
```
This scree plot helps us to decide the best k; in other words, the number of 
thread colors we are going to use for the stitch pattern. This step is very 
siginificant because we do not want similar colors, or not enough colors. A k 
that is too large will not help us better illutrate the image in the cross-stitich 
pattern. A small k will result in not enough thread colors to display the original 
picture. According to the scree plot above, six will be a good choice because the 
total with in cluster sum of squares stops to decrease as much.

Next, the colour_strips() function simply demonstrates the DMC thread colors for 
each k in the k_list.
```{r}
colour_strips(cluster_info)
```

Finally, we can plot the cross-stitich pattern by using the make_pattern() 
function. The function takes in cluster_info, choice of k, and size of the 
pattern as input. In addition, The function produce a colored pattern by default.
You can add black_white = TRUE in the input to produce a black and white pattern. 
You can also add a background_color = "the color you want" to change the 
background color of the pattern.
```{r}
make_pattern(cluster_info, 6, 50)
```
```{r}
make_pattern(cluster_info, 6, 50, black_white = TRUE)
```
```{r}
make_pattern(cluster_info, 6, 50, background_colour = "yellow")
```
Unfortunately, the function cannot produce the pattern in the right matching DMC 
thread colors and display the color name in the legend.
